Grove: A Convergent Collaborative Structure-Editor Calculus

### 2020-07-20 grove-paper.tex
Updates from Overleaf

Supporting this kind of behavior is

Explain that can continue editing orphans

@@

A and B both insert different expressions into the same hole

Formal conflict doesn't nessisarily mean a UI conflict.
Mention resolution algorithms and that we discuss idioms
as automatic quick fixes

>>>>

A consequence of this design is that we allow users to edit
parts of the code that have been deleted.  For example,
Alice might receive Bob's deletion of edge~7 before making her
edits and before receiving Bob's adding of edge~16.
Her edits would then be within the code deleted by Bob.

TODO:figure

Contrast this

@@

Finally, we address genuine conflicts between edits.
Consider the top graph of Figure~\ref{fig:Direct Conflicts}.
Suppose Alice inserts the number literal \texttt{2} into the body of the lambda
while Bob inserts the function application \texttt{f x} also into the body of the lambda.
These results in the left and right graphs of \ref{fig:Direct Conflicts} respectively.
In particular pay attention to the edges going out of the \texttt{body} index of node~3.
In the left graph it is edge~10, which points to a number literal,
and in the right graph it is edge~13, which points to a function application.

We merge these by including \emph{both} edges as edges going out of the \texttt{body} index
of node~3.
This results in the bottom graph of Figure~\ref{fig:Direct Conflicts}.
The conflict between Alice's and Bob's changes is
represented by the fact that there are multiple edges going out of one index (i.e. the \texttt{body}
index of node~3).
In the graph representation, we flag this conflict by highlighting its edges
in red.
In the textual representation, we flag this conflict with the notation \texttt{\{ 2 | f x \}}.
This is a conflict that much eventually be resolved by the user by deleting
one of the edges and editing the other to be the merged value.
For example, one could delete edge~10 and then edit the \texttt{x}
to be \texttt{x + 2}.
Note that users can continue to edit the code while in this conflicted state.
It just must be resolved before the the code can be run.\footnote{
It may be possible to develop evaluation models that allow these sorts of conflicts,
but that is beyond the scope of this paper.}.

Note that as a convenience to the user, certain simple
conflicts might be automatically resolved,
but we consider this a higher-level, user-interface consideration.

TODO: need example of fully-automatic resolution and semi-automatic resolution
